---
title: "Statistical inference"
author: "Saurabh Yadav"
output: pdf_document
---
##PART1-A Simulation Excersise

##

####Simulating exponantial variables
```{r}
library(ggplot2)
n<-1000
col<-40
expovar<-rexp(n*col,0.2)
```

####creating matrix for the exponantial variables
```{r}
mat<-matrix(expovar,n,col)
```
####taking the mean of the 40 exponantial variables
```{r}
expomean<-apply(mat, 1, mean)
```

###Comparisons
####Comparison between sample mean and the theoretical mean
#### 1.mean of the population
```{r}
mean(expovar)
```

####plotting the distribution of averages
```{r}
ggplot(data.frame(expomean),aes(expomean))+geom_histogram(aes(y=..density..),col="black",fill="steelblue")+geom_density(col="black")+geom_vline(aes(xintercept=mean(expomean, na.rm=T)))+labs(x="averages of 40 variables")
```


###RESULT

####1.The plot shows the distribution of averages is normally distributed and follows the Central Limit Theorm

####2.The population mean and the mean of averages are approximate beacause the plot is centered around the population mean


